A Comparison of Parallel Graph Processing Benchmarks

### 2017-02-16 papers/publication/paper-pollard.tex
Added the RAM figure (though not in repository).

\begin{figure}
	\centering
	\begin{minipage}{0.48\linewidth}
		\includegraphics[width=\linewidth, trim=0 36pt 18pt 0, clip]{graphics/pr_time.pdf}
	\end{minipage}
	\begin{minipage}{0.48\linewidth}
		\includegraphics[width=\linewidth, trim=0 36pt 18pt 0, clip]{graphics/pr_iters.pdf}
	\end{minipage}
	\caption{[TODO: Rerun PowerGraph] The $y$-axis is logarithmic. GraphMat iterations are measured differently because of the ``think like a vertex'' paradigm and runs until none of the vertices' ranks change.}
	\label{fig:pr}
\end{figure}

@@

>>>>

\begin{figure}
	\centering
	\begin{minipage}{0.48\linewidth}
		\includegraphics[width=\linewidth, trim=0 24pt 18pt 0, clip]{graphics/pr_time.pdf}
	\end{minipage}
	\begin{minipage}{0.48\linewidth}
		\includegraphics[width=\linewidth, trim=0 24pt 18pt 0, clip]{graphics/pr_iters.pdf}
	\end{minipage}
	\caption{The $y$-axis is logarithmic. GraphMat iterations are measured differently because of the ``think like a vertex'' paradigm and runs until none of the vertices' ranks change.}
	\label{fig:pr}
\end{figure}

@@

RAPL also allows the measurement of DRAM power and energy, whose results are shown in Fig.~\ref{fig:ram-power}.

\begin{figure}
	\centering
	\includegraphics[width=0.6\linewidth, trim=0 36pt 18pt 0, clip]{graphics/bfs_ram_power.pdf}
	\caption{RAM Power Consumption, averaged across all roots. [TODO: Explain more]}
	\label{fig:ram-power}
\end{figure}
